\subsection{Standard System Functions}
\texttt{{\large\textbf{to\_int}}}\textsf{(any):integer}\\
 Converts the argument to an integer value.

\hrulefill

\texttt{{\large\textbf{to\_real}}}\textsf{(any):real}\\
 Converts the argument to a real number (double precision).

\hrulefill

\texttt{{\large\textbf{to\_bool}}}\textsf{(any):boolean}\\
 Converts the argument to a boolean value (1=true, 0=false).

\hrulefill

\texttt{{\large\textbf{to\_string}}}\textsf{([any]):string}\\
 Converts the argument[s] to a text string.

\hrulefill

\texttt{{\large\textbf{alloc}}}\textsf{(integer, \{integer\}):array}\\
 Allocates an array of one or two dimensions.

\hrulefill

\texttt{{\large\textbf{dir\_list}}}\textsf{(string:path, string:extensions, [boolean:list dirs also]):array}\\
 List all the files in a directory. The extensions parameter is a comma separated list of extensions, or * to retrieve every item.

\hrulefill

\texttt{{\large\textbf{file\_exists}}}\textsf{(string):boolean}\\
 Determines whether a file exists or not.

\hrulefill

\texttt{{\large\textbf{dir\_exists}}}\textsf{(string):boolean}\\
 Determines whether the specified directory exists.

\hrulefill

\texttt{{\large\textbf{rename\_file}}}\textsf{(string:old name, string:new name):boolean}\\
 Renames an existing file.

\hrulefill

\texttt{{\large\textbf{remove\_file}}}\textsf{(string):boolean}\\
 Deletes the specified file from the filesystem.

\hrulefill

\texttt{{\large\textbf{mkdir}}}\textsf{(string:path, \{boolean:make\_full=true\}):boolean}\\
 Creates the specified directory, optionally creating directories as need for the full path.

\hrulefill

\texttt{{\large\textbf{path\_only}}}\textsf{(string):string}\\
 Returns the path portion of a complete file path.

\hrulefill

\texttt{{\large\textbf{file\_only}}}\textsf{(string):string}\\
 Returns the file name portion of a complete file path, including extension.

\hrulefill

\texttt{{\large\textbf{ext\_only}}}\textsf{(string):string}\\
 Returns the extension of a file name.

\hrulefill

\texttt{{\large\textbf{cwd}}}\textsf{(void):string}\\
 Returns the current working directory.

\texttt{{\large\textbf{cwd}}}\textsf{(string):boolean}\\
 Sets the current working directory.

\emph{Notes:} Two modes of operation: set or retrieve the current working directory.

\hrulefill

\texttt{{\large\textbf{system}}}\textsf{(string):integer}\\
 Executes the system command specified, and returns the exit code.

\hrulefill

\texttt{{\large\textbf{write\_text\_file}}}\textsf{(string:file, string:data):boolean}\\
 Writes data to a text file.

\hrulefill

\texttt{{\large\textbf{read\_text\_file}}}\textsf{(string:file):string}\\
 Reads the entire contents of the specified text file and returns the result.

\hrulefill

\texttt{{\large\textbf{open}}}\textsf{(string:file, string:rwa):integer}\\
 Opens a file for 'r'eading, 'w'riting, or 'a'ppending.

\hrulefill

\texttt{{\large\textbf{close}}}\textsf{(integer:filenum):void}\\
 Closes an open file.

\hrulefill

\texttt{{\large\textbf{seek}}}\textsf{(integer:filenum, integer:offset, integer:origin):integer}\\
 Seeks to a position in an open file.

\hrulefill

\texttt{{\large\textbf{tell}}}\textsf{(integer:filenum):integer}\\
 Returns the current value of the file position indicator.

\hrulefill

\texttt{{\large\textbf{eof}}}\textsf{(integer:filenum):boolean}\\
 Determines whether the end of a file has been reached.

\hrulefill

\texttt{{\large\textbf{flush}}}\textsf{(integer:filenum):void}\\
 Flushes the file output stream to disk.

\hrulefill

\texttt{{\large\textbf{read\_line}}}\textsf{(integer:filenum, @string:buffer):boolean}\\
 Reads one line of text from a file, returning whether there are more lines to read.

\hrulefill

\texttt{{\large\textbf{write\_line}}}\textsf{(integer:filenum, string:dataline):boolean}\\
 Writes one line of text to a file.

\hrulefill

\texttt{{\large\textbf{read}}}\textsf{(integer:filenum, @string:buffer, integer:bytes):boolean}\\
 Reads data from a file, returning false if there is no more data to read.

\hrulefill

\texttt{{\large\textbf{write}}}\textsf{(integer:filenum, string:buffer, integer:bytes):boolean}\\
 Writes data to a file.

\hrulefill

\texttt{{\large\textbf{load\_extension}}}\textsf{(string:path):boolean}\\
 Loads an LK extension library.

\hrulefill

\texttt{{\large\textbf{extensions}}}\textsf{(none):table}\\
 Returns information about currently loaded extensions

\hrulefill

\texttt{{\large\textbf{ostype}}}\textsf{(none):string}\\
 Returns identifying information about the operating system type. ('osx', 'win32', 'linux', etc).
